\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[black]{casual}                  % optional argument are 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% Hyperlinks
%\usepackage{hyperref}								% to use hyperlinks
%\definecolor{linkcolour}{rgb}{0,0.2,0.6}			% hyperlinks setup
%\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

% personal data
\firstname{Donald}
\familyname{Huang}
%\title{Resumé title (optional)}               % optional, remove the line if not wanted
\address{1080 Sutter St Apt 603}{San Francisco, CA 94109}    % optional, remove the line if not wanted
%\mobile{+30 698 4385057}                    % optional, remove the line if not wanted
\phone{412-641-9102}                      % optional, remove the line if not wanted
%\fax{fax (optional)}                          % optional, remove the line if not wanted
\email{don.hcd@gmail.com}                      % optional, remove the line if not wanted
%\email{\href{mailto:s.dakourou@gmail.com}{s.dakourou@gmail.com}}                      % optional, remove the line if not wanted
%\homepage{\href{http://gr.linkedin.com/pub/stefania-dakourou/41/21a/396}{LinkedIn Profile}}                % optional, remove the line if not wanted
\extrainfo{\href{http://github.com/donhcd}{github.com/donhcd}} % optional, remove the line if not wanted
%\photo[64pt][0.4pt]{picture}                         % '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Some quote (optional)}                 % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Work Experience}
\cventry{Oct 2014 - Present}{Software Engineer}{Docker, Inc.}{San Francisco,
CA}{}{\begin{itemize}\item Worked on the Docker Trusted Registry, Docker's on-premise Docker
registry solution.\item Designed and implemented the original architecture,
upgrades, and search and worked on making the Trusted Registry highly available.
\item Worked with open source to file issues and sometimes fixes.\end{itemize}}
\cventry{Jan-Sept 2014}{Software Engineer}{Koality Code}{San Francisco, CA}{}{Worked on building an on-premise CI solution in Go. Koality Code was acquired by Docker in October.}
\cventry{2013}{Software Engineer}{Gumroad}{San Francisco, CA}{}{Worked on both backend and frontend in building a new gifting feature and a new API}
\cventry{2012}{15-213 Teaching Assistant}{Carnegie Mellon University}{Pittsburgh, PA}{}{Introduction to Computer Systems: an introduction to C and systems programming.}
\cventry{2012}{Software Engineer Intern}{Facebook}{Menlo Park, CA}{}{Worked on voice messaging in the Android client for Facebook Messenger.}

\section{Relevant Coursework}
\cventry{Spring 2012}{15-410 Operating System Design and Implementation}{}{}{}{Worked with a partner to write a threading library implementing \texttt{thr\_create()}, \texttt{thr\_join()}, and \texttt{thr\_exit()}, along with mutexes, condition variables, and semaphores, in C.\\Wrote a robust stack trace printer in C.}

\section{Past Projects}
\cventry{Spring 2013}{popkorn.me (Now defunct)}{PennApps}{}{}{Worked with 3 other students to create a collaborative Youtube video viewer.}
\cventry{Spring 2013}{scheduleplus.org}{}{}{}{A site where students can see what courses their classmates are taking. Built the ``heatmap'' feature where users can view many people's schedules simultaneously in order to choose optimal meeting times}

\section{Skills}
\cvline{Programming Languages}{Golang, C, Java/Android, Haskell, Javascript, Python, Rails, Standard ML, Clojure}
\cvline{Software}{GNU utils, vim, git, bash, Intellij}

\section{Education}
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}
\cventry{2014}{Bachelors in Computer Science}{Carnegie Mellon University}{Pittsburgh, PA}{}{}

\end{document}
